### 2019-01-30 README.Rmd
update pkgdown with icon
valid minimal example in README

@@

# EML

@@

```{r}
me <- list(individualName = list(givenName = "Carl", surName = "Boettiger"), id="cboettig")
my_eml <- list(dataset = list(
              title = "A Mimimal Valid EML Dataset",
              creator = me,
              contact = me)
            )

>>>>

# EML <img src="man/figures/logo.svg" align="right" alt="" width="120" />

@@

@@

```{r}
me <- list(individualName = list(givenName = "Carl", surName = "Boettiger"))
my_eml <- list(dataset = list(
              title = "A Mimimal Valid EML Dataset",
              creator = me,
              contact = me)
            )
